Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-14 ms.qmd
Fixed orchard plot - removed ata argument. Models mostly all rerun

p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat", data = lnRRQ10_data_wild_acclim, ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 5) + 
geom_text(data = dat_text2, aes(x = x, y = y-0.3, label = label2), size = 5) +
geom_text(data = dat_text2, aes(x = x, y = y-0.65, label = p), size = 5) +
theme(legend.position = "bottom", 
      strip.background = element_blank(), 
      strip.text = element_blank(), 
      axis.text = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16))

>>>>

p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text2, aes(x = x, y = y, label = label), size = 5) + 
geom_text(data = dat_text2, aes(x = x, y = y-0.3, label = label2), size = 5) +
geom_text(data = dat_text2, aes(x = x, y = y-0.65, label = p), size = 5) +
theme(legend.position = "bottom", 
      strip.background = element_blank(), 
      strip.text = element_blank(), 
      axis.text = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16))
